---
title: "data_transform"
author: "Vaishnavi Behl"
date: "AT 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

### Question 1

## Function Documentation 

This document loads the Iris dataset and explains how to use the `calculate_mean_sepal_length` function with the dataset.


## Function Overview 

The `calculate_mean_sepal_length` function calculates the mean sepal length for a specific species of iris flowers in the "iris" dataset.

```{r}
# Load the "iris" dataset
data(iris)

# Initial function to calculate mean sepal length for a specific species 
calculate_mean_sepal_length <- function(species) {
  subset_data <- iris[iris$Species == species, ]
  return(mean(subset_data$Sepal.Length))
}

```

## Function Usage

To use the function, call it with the `species` argument to specify the iris species you are interested in:

```{r}

# Calculate the mean sepal length for the setosa species

calculate_mean_sepal_length(species = "setosa")

# Calculate the mean sepal length for the virginica species
calculate_mean_sepal_length(species = "virginica")

```


## Updated Function 

```{r}

# Updated function to calculate mean sepal length for a specific species and number of observations
calculate_mean_sepal_length <- function(species, n = NULL) {
  subset_data <- subset(iris, Species == species)
  
  if (!is.null(n)) {
    subset_data <- subset_data[1:min(n, nrow(subset_data)), ]
  }
  
  return(mean(subset_data$Sepal.Length))
}

```


## Demonstrating the usage of the updated function

```{r}
# Calculate the mean sepal length for the first 3 observations of setosa
calculate_mean_sepal_length(species = "setosa", n = 3)

```

## Appendix: All code in this assignment

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE} 

```
