---
title: "Data Transformation Documentation"
author: "Vaishnavi Behl"
date: "AT 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

### Function Documentation

This document explains how to use the calculate_mean_sepal_length function with the Iris dataset. It provides details about the function, its parameters, and usage.


## Function Overview 

The calculate_mean_sepal_length function calculates the mean sepal length for a specific species of iris flowers in the "iris" dataset.

```{r}
# Load the "iris" dataset
data(iris)

# Function to calculate mean sepal length for a specific species
calculate_mean_sepal_length <- function(species) {
  subset_data <- iris[iris$Species == species, ]
  return(mean(subset_data$Sepal.Length))
}

```

## Function Usage 

To use the function, call it with the species argument to specify the iris species you are interested in:

```{r}
# Calculate the mean sepal length for the setosa species
calculate_mean_sepal_length(species = "setosa")

# Calculate the mean sepal length for the virginica species
calculate_mean_sepal_length(species = "virginica")

```

## Updated Function

An updated version of the function is provided below. It now allows you to specify the number of observations to consider. If n is provided, the function calculates the mean sepal length for the specified number of observations. If n is not provided, it calculates the mean sepal length for all observations of the specified species.

```{r}

# Updated function to calculate mean sepal length for a specific species and number of observations

calculate_mean_sepal_length <- function(species, n = NULL) {
  subset_data <- subset(iris, Species == species)
  
  if (!is.null(n)) {
    subset_data <- subset_data[1:min(n, nrow(subset_data)), ]
  }
  
  return(mean(subset_data$Sepal.Length))
}
```

## Demonstrating the usage of the updated function

You can now specify the number of observations to consider when calculating the mean sepal length. For example, to calculate the mean sepal length for the first 3 observations of setosa:

```{r}

calculate_mean_sepal_length(species = "setosa", n = 3)

```

## Appendix: All code in this assignment

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE} 

```
