---
title: "data_transform"
author: "Vaishnavi Behl"
date: "AT 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


# Function Documentation 

This document loads the Iris dataset and explains how to use the `calculate_mean_sepal_length` function with the dataset.


#Function Overview 

The `calculate_mean_sepal_length` function calculates the mean sepal length for a specific species of iris flowers in the "iris" dataset.

```{r}
# Load the "iris" dataset
data(iris)

# Initial function to calculate mean sepal length for all species
calculate_mean_sepal_length <- function(species) {
  return(mean(iris$Sepal.Length))
}

```

## Function Usage

To use the function, call it with the `species` argument to specify the iris species you are interested in:

```{r}

# Calculate the mean sepal length for the setosa species

calculate_mean_sepal_length(species = "setosa")

# Calculate the mean sepal length for the virginica species
calculate_mean_sepal_length(species = "virginica")

```


